\documentclass[./doc.tex]{subfiles}
\begin{document}

\section{Subroutines}

\subsection{BRTSGN}
Compute the Bierman modified R-T-S smooth gain factors for colored noise model
\begin{gather}
    \bm{X}_{T+}=\bm{\Phi}_M \bm{X}_{T-} + \bm{BW}_{T} \\
    \bm{\Phi}_M=\bm{I} + (M-1)\bm{E}_{ip}\bm{E}_{ip}^{\textrm{T}} \\
    \bm{E}_{ip}(j)=\begin{cases}
        0 & j \ne ip \\
        1 & j = ip
    \end{cases}
\end{gather}

Calls: GIVENS

\subsection{C2C}
Rearrange a parameters list-associated matrix according to a given list of parameters.

\subsection{CNS}
Colored Noise UD Smoother

Calls: UDGEN

\subsection{CNSUD}
Colored Noise Smooth U-D covariance factor update to account for possible off-diagonal
process noise components.

Dynamic model
\begin{equation}
    \begin{bmatrix}
        \bm{X}_{i+1} \\
        p_{i+1}      \\
        \bm{Y}
    \end{bmatrix} =
    \begin{bmatrix}
        \bm{I} & 0  & \bm{0} \\
        \bm{0} & EM & \bm{0} \\
        \bm{0} & 0  & \bm{I}
    \end{bmatrix}
    \begin{bmatrix}
        \bm{X}_{i} \\
        p_{i}      \\
        \bm{Y}
    \end{bmatrix} +
    \begin{bmatrix}
        \bm{B}_{\bm{X}} \\
        1               \\
        \bm{0}
    \end{bmatrix} W_i
\end{equation}

Calls: UDOPT, UCON, RNK1

\subsection{CNSX}
Colored Noise Smoothing algorithm estimate update, from time \(t\) back to time \(t-dt\).

\subsection{CNSXUD}
Colored Noise Smoothing algorithm estimate update, simple process noise component
adjustment, from time \(t\) back to time \(t-dt\).

Process noise model multiplier matrix \(\bm{B}_{\bm{X}/j}\),
\begin{equation}
    \bm{X}_{j+1} = \bm{\Phi}_{\bm{X}} \bm{X}_j + \bm{B}_{\bm{X}/1} W_{j}(1) + \cdots + \bm{B}_{\bm{X}/N_p} W_{j}(N_p)
\end{equation}
where \(W_j\) are the process noise components.

\subsection{COV2RI}
Construct the upper triangular Cholesky factor \(\bm{U}\) of a positive semi-definite covariance matrix
\(\bm{P}\) (note that \(\bm{P}\) is symmetric), i.e.,
\begin{equation}
    \bm{P}=\bm{U}\bm{U}^{\textrm{T}}
\end{equation}

\subsection{COV2UD}
Construct the U-D factors \(\bm{U}\) and \(\bm{D}\) of a positive semi-definite covariance matrix
\(\bm{P}\) (note that \(\bm{P}\) is symmetric), i.e.,
\begin{equation}
    \bm{P}=\bm{U}\bm{D}\bm{U}^{\textrm{T}}
\end{equation}

\subsection{COVCOR}
Compute the correlation matrix \(\bm{\rho}\) for a covariance matrix \(\bm{P}\), \(\rho_{ij}=P_{ij}/(\sqrt{P_{ii}P_{jj}})\).

\subsection{D2U}
Update a contiguous part of the diagonal elements of a U-D factor, i.e., \(\bm{D}\).

\subsection{GIVENS}
Given an vector \([a \thickspace b]^\textrm{T}\), compute the Givens rotation parameters \(c\), \(s\) and \(\sigma\) so that
\begin{equation}
    \begin{bmatrix*}[r]
        c & s \\
        s & -c
    \end{bmatrix*}
    \begin{bmatrix}
        a \\
        b
    \end{bmatrix} = \begin{bmatrix}
        \sigma \\
        0
    \end{bmatrix}
\end{equation}

\subsection{HHPOST}
Triangularize a rectangular matrix by orthogonal transformation.

\subsection{INF2R}
Compute the Cholesky factor for an information matrix.

\subsection{INVTST}
Compute the measurement innovations variance \( \alpha = H\bm{P}H^{\textrm{T}} + R\) using the
U-D covariance factors of \(\bm{P}\).

\subsection{LISPOS}
Search a string list for a given string.

\subsection{MAPU}
Compute mapped covariance \(\bm{P}_{\textrm{out}}=(\bm{\Phi}\bm{U})\bm{D}(\bm{\Phi}\bm{U})^{\textrm{T}}\).

Calls: PHIU

\subsection{P2P}
Similar to C2C.

\subsection{PERMUT}
Similar to C2C.

\subsection{PHIU}
Compute \(\bm{W}=\bm{\Phi}\bm{U}\) where \(\bm{\Phi}\) is a rectangular matrix with implicitly
defined columns of trailing zeros and \(\bm{U}\) is a vector stored upper triangular matrix.

\subsection{PINVB}
Compute solution \(\bm{v}\) to equation \(\bm{P}\bm{v}=\bm{B}\) where \(\bm{P}=\bm{U}\bm{D}\bm{U}^{\textrm{T}}\).

\subsection{PINVBM}
Compute solution \(\bm{v}\) to equation \(\bm{P}\bm{v}=\bm{BM}\) where
\(\bm{P}=\bm{U}\bm{D}\bm{U}^{\textrm{T}}\) and \(BM(j)=EM\times B(j), j=1,\cdots, N_x\).

Calls: U2SIG

\subsection{PINVEK}
Compute solution \(\bm{v}\) to equation \(\bm{P}\bm{v}=\bm{E}_k\) where
\(\bm{P}=\bm{U}\bm{D}\bm{U}^{\textrm{T}}\) and \(\bm{E}_k\) has unity in element \(k\), i.e.,
compute column \(k\) of \(\bm{P}^{-1}\).

\subsection{R2A}
Restore a vector-stored triangular matrix \(\bm{R}\) to a 2-D matrix \(\bm{A}\) and
arrange the columns to match the given parameters list.

\subsection{RA}
Partly compute the product \(\bm{W}=\bm{R}\bm{A}\) where \(\bm{R}\) is a vector-stored triangular
matrix.

\subsection{RANK1/RNK1}
Rank one modification of the Cholesky Factorization, i.e., Agee-Turner PD Factorization uodate
\(\bm{\bar{U}} \bm{\bar{D}} \bm{\bar{U}}^{\textrm{T}}=\bm{U} \bm{D} \bm{U}^{\textrm{T}} + c \bm{a} \bm{a}^{\textrm{T}}\).

\subsection{RCOLRD}
Add in Markov colored noise model effects into the Square Root Information Filter (SRIF), and generate weighting
coefficients for smoothing. Each component in the state variables vector \(\bm{X}\) satisfies
\(x_{j+1} = e_M x_j + w_j\), where \(e_M\) is the colored noise mapping coefficient (generally of exponential
form, \(e_M = e^{-dt/\tau}\)).

\subsection{RI2COV}
Compute the standard deviations and, if desired, the covariance matrix of a vector stored upper triangular
square root covariance matrix.

\subsection{RINCON}
Compute the inverse of an upper triangular vector stored matrix and its condition number estimate.

\subsection{RINZ}
Compute the solution vector \(\bm{x}\) to the matrix equation \(\bm{R} \bm{x} = \bm{Z}\), where
\(\bm{R}\) is an upper triangular vector stored matrix.

\subsection{RL2RU}
Copy the lower right portion of a vector stored upper triangular matrix into the upper left corner
block of another vector stored upper triangular matrix.

\subsection{RMPRNT}
Print a rectangular vector stored matrix.

\subsection{RTMSX}
Multiply a vector stored matrix with a vector, i.e., calculate \(\bm{R}\bm{x}\).

\subsection{RU2RL}
Copy the upper left portion of a vector stored upper triangular matrix into the lower right corner
block of another vector stored upper triangular matrix.

\subsection{RUDR}
Transform an upper triangular vector stored SRIF matrix to UD form or vice versa.

Calls: RINCON

\subsection{SDOT1}
Calculte the dot product of
\begin{equation}
    \sum_{i=0}^{N-1} S_x(l_x + i \cdot inc_x) \cdot S_y(l_y + i \cdot inc_y)
\end{equation}
where \(l_x=1\) if \(inc_x \ge 0\). Otherwise, \(l_x=(-inc_x) \cdot N\). \(l_y\) is defined in a similar way using \(inc_y\).

\subsection{SFU}
Compute \(\bm{W}=\bm{F} \bm{U}\) where \(\bm{F}\) is a sparse matrix with only the non-zero elements are defined,
and \(\bm{U}\) is a vector-stored upper triangular matrix with implicitly defined unit diagonal elements.

\subsection{SGDCMP}
Compute and display the U-D sigma decomposition associated with the covariance matrix
\(\bm{UD}\bm{U}^{\textrm{T}}\).

Calls: RMPRNT, TMPRNT

\subsection{SINTST}
Compute the measurement prediction (innovations) variance,
\begin{equation}
    \alpha = \bm{H}\bm{R}^{-1}\bm{R}^{-\textrm{T}}\bm{H}^{\textrm{T}} + 1
\end{equation}

\subsection{STPHIU}
Compute \(\bm{\Phi}\cdot \bm{U}\) where \(\bm{\Phi}\) is an unit triangular sparse matrix and \(\bm{U}\) is
a vector stored upper triangular matrix with implicitly defined unit diagonal elements.

\end{document}